02_LH-SIP_Quantification

### 2022-05-24 02_LH-SIP_Quantification.Rmd
added RDS extension and memcorr turnover

```{r}
turnover <- LH_SIP_data %>% 
  # Combine 0d --> and 3d --> datasets
  bind_rows(LH_SIP_data_3d_onwards) %>% 
  # Evaluate each row individually
  ungroup() %>%
  mutate(
    # Explicitly define incubation parameters:
    f_label = F_label_mn, # actual measured F_L
    t0 = 0, # incubation start = 0
    d_t = inc_time_d - t0, # change in time
    f_start = at2H_mn_zero,
    f_start_mc = at2H_mn_zero_mc,
    # use PAME-corrected 2F value
    f_t = `2F_alk`,
    f_t_mc = `2F_alk_mc`, # memory corrected value
    # delta 2F: change in 2F enrichment over time t
    dF = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),
    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
    u_d = calculate_turnover(
      a = a, # Assimilation efficiency defined in data reduction step
      FT = f_t, # 2F at time t (at%)
      F0 = f_start, # 2F at t0 (at%)
      FL = f_label, # 2F of label (at%)
      t = d_t # change in time
      ),

@@

    # And a memory-corrected turnover:
    u_d_mc = calculate_turnover(
      a = a, # Assimilation efficiency defined in data reduction step
      FT = f_t_mc, # 2F at time t (at%) (memory corrected)
      F0 = f_start, # 2F at t0 (at%)
      FL = f_label, # 2F of label (at%)
      t = d_t # change in time
      ),

@@

```{r}
# Create a summarized dataframe grouped by experimental replicates
turnover_summarized <- turnover %>% 
  group_by(
    time_course,
    terrain, 
    inc_time_d,
    compound
  ) %>% 
  dplyr::summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  )

# Summarize by combining experimental replicates

LH_SIP_data_summarized <- LH_SIP_data %>% 
  group_by(
    terrain, 
    inc_time_d, 
    compound
  ) %>% 
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  )

@@

    # Keep these:
    f_label = mean(F_label_mn, na.rm = TRUE),
    a = 0.6,
    t0 = 0,
    d_t = inc_time_d - t0, # change in time
    f_start = mean(at2H_mn_zero, na.rm = TRUE),
    f_t = `2F_alk_weighted`,
    f_t_mc = `2F_alk_mc_weighted`,

    dF_weighted = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),
    #Do the same for memory-corrected data:
    dF_weighted_mc = case_when(
      f_t_mc - f_start >= 0 ~ f_t_mc - f_start,
      f_t_mc - f_start < 0 ~ 0),

  ) %>%
  dplyr::summarize_if(
    is.numeric,
    mean,
    na.rm = TRUE
  ) %>%
  mutate(
    u_d_weighted = calculate_turnover(
      a = a,
      FT = f_t,
      F0 = f_start,
      FL = f_label,
      t = d_t
    ),
    gen_d_weighted = turnover_to_gen(u_d_weighted),
    # Do the same for memory corrected data
    u_d_mc_weighted = calculate_turnover(
      a = a,
      FT = f_t_mc,
      F0 = f_start,
      FL = f_label,
      t = d_t
    ),
    gen_d_mc_weighted = turnover_to_gen(u_d_mc_weighted),
  )
```

# Export
```{r}
turnover %>% saveRDS(file = "cache/turnover_rates")

turnover_summarized %>% saveRDS(file = "cache/turnover_summarized")

weighted_time_course %>% saveRDS(file = "cache/turnover_weighted")
```

>>>>

```{r}
turnover <- LH_SIP_data %>% 
  # Combine 0d --> and 3d --> datasets
  # Evaluate each row individually
  ungroup() %>%
  mutate(
    # Explicitly define incubation parameters:
    f_label = F_label_mn, # actual measured F_L
    t0 = 0, # incubation start = 0
    d_t = inc_time_d - t0, # change in time
    f_start = at2H_mn_zero,
    f_start_mc = at2H_mn_zero_mc,
    # use PAME-corrected 2F value
    f_t = `2F_alk`,
    f_t_mc = `2F_alk_mc`, # memory corrected value
    # delta 2F: change in 2F enrichment over time t
    dF = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),
    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
    u_d = calculate_turnover(
      a = a, # Assimilation efficiency defined in data reduction step
      FT = f_t, # 2F at time t (at%)
      F0 = f_start, # 2F at t0 (at%)
      FL = f_label, # 2F of label (at%)
      t = d_t # change in time
      ),

@@

    # And a memory-corrected turnover:
    u_d_mc = calculate_turnover(
      a = a, # Assimilation efficiency defined in data reduction step
      FT = f_t_mc, # 2F at time t (at%) (memory corrected)
      F0 = f_start_mc, # 2F at t0 (at%)
      FL = f_label, # 2F of label (at%)
      t = d_t # change in time
      ),

@@

## Summarize turnover by experimental replicates

```{r}
turnover_summarized <- turnover %>% 
  group_by(
    terrain, 
    inc_time_d,
    compound
  ) %>% 
  dplyr::summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  )

```

## Summarize 2F by experimental replicates

```{r}

LH_SIP_data_summarized <- LH_SIP_data %>% 
  group_by(
    terrain, 
    inc_time_d, 
    compound
  ) %>% 
  # Filter out long-chain compounds
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  )

```

## Weight values by abundance (rel_area_FID)

```{r}

@@

    # Keep these:
    f_label = mean(F_label_mn, na.rm = TRUE),
    a = 0.6,
    t0 = 0,
    d_t = inc_time_d - t0, # change in time
    f_start = mean(at2H_mn_zero, na.rm = TRUE),
    f_start_mc = mean(at2H_weighted_mc, na.rm = TRUE),
    f_t = `2F_alk_weighted`,
    f_t_mc = `2F_alk_mc_weighted`,

    dF_weighted = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),

    #Do the same for memory-corrected data:
    dF_weighted_mc = case_when(
      f_t_mc - f_start_mc >= 0 ~ f_t_mc - f_start_mc,
      f_t_mc - f_start_mc < 0 ~ 0),

  ) %>%
  dplyr::summarize_if(
    is.numeric,
    mean,
    na.rm = TRUE
  ) %>%
  mutate(
    u_d_weighted = calculate_turnover(
      a = a,
      FT = f_t,
      F0 = f_start,
      FL = f_label,
      t = d_t
    ),
    gen_d_weighted = turnover_to_gen(u_d_weighted),
    # Do the same for memory corrected data
    u_d_mc_weighted = calculate_turnover(
      a = a,
      FT = f_t_mc,
      F0 = f_start_mc,
      FL = f_label,
      t = d_t
    ),
    gen_d_mc_weighted = turnover_to_gen(u_d_mc_weighted),
  )
```

# Export
```{r}
turnover %>% saveRDS(file = "cache/turnover_rates.RDS")

turnover_summarized %>% saveRDS(file = "cache/turnover_summarized.RDS")

weighted_time_course %>% saveRDS(file = "cache/turnover_weighted.RDS")
```
